Reply To Examiners

### 2014-04-29 answer_thesis_examiner/chap2.tex
auto

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\
9 & 7 & multidimensional & Multi-dimensional \\
10 & 12 & The model os & The model is \\
11 & 28 & chapter 5 & Chapter 5 \\
12 & 6 & chapter 6 & Chapter 6 \\
22 & 15 & RadarSat & RadarSat-2 \\
24 & 14 & SVM & SVM (Support Vector Machine) \\
35 & 6-7 & Rician distribution [48]... & Rician distribution [48]. \\
35 & 11 & back scattering & backscattering \\
36 & 10 & literatured & literatures \\
37 & -2 & Proposed bu & proposed by \\
39 & 4 & dependence & dependency \\
44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
46 & 4 & most known common & most commonly known \\
56 & 6 & POLSAR And & POLSAR. And \\
65 &5,7 & an homogeneous area & a homogeneous area \\
77 & 3 & the objective then is & the objective is \\
77 & 5,6 & it has already been proven & it has already been proven [?] \\
87 & -1 & Fig 5.6a & Fig 5.6. \\
89 & - & Figure 5.6 - subtitle (a) & (a) is removed \\
91 & - & Figure 5.8: Legends are too small to read & They are enlarged \\
95 & - & Figure 5.12 & Use the same scale for  y axis (i.e MSE 0:1) across all the plots \\
103 & 22 & related to the ENL index. over & related to the ENL index over \\
104 & 13 & Equation 5.3.2.1 & The number is corrected to (?) \\
109 & 8 & Figs. 5.21c and 5.21d allows & Fig 5.21(a) and Fig 5.21(d) allow \\
112 & 13 & these smaller requirements & these requirements \\
132 & 9 & evaluation criteria & evaluation criterion
\end{longtable}

@@

In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
I also feel indebted to the Examiner with his suggestion to extract out and submit portions of this thesis as scientific papers for peer review.

>>>>

\replyToComment
    {Replace the word ``theory'' with ``model'' throughout the thesis}
    {Search and replace operation done!}

\replyToComment
    {The proposed model is derived based on the existing statistical models for SAR and extended to POLSAR}
    {The main approach, as described in the thesis, differs in a subtle but important way.
The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
That is: the proposed models by nature are applicable to multi-dimensional data and thus they are applicable to POLSAR data.
To show that the proposed models are also applicable to SAR data, the dimension parameters in these models are collapsed into 1.
The thesis subsequently shows that they match perfectly with existing SAR models.
}

\replyToComment
    {The proposed log-transform model will introduce an inevitable bias error, which may not be able to measure by MSE.}
    {
      The thesis clearly recognizes that log-transformation will introduce bias.
      It also shows that MSE evaluation does inherently include bias evaluation.
      In fact, the thesis argues that MSE evaluation has two components: 1. bias evaluation and 2. variance evaluation, which for evaluating the performance of SAR speckle filters translates into 1. radiometric preservation and 2. noise suppression respectively.
}

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\
9 & 7 & multidimensional & Multi-dimensional \\
10 & 12 & The model os & The model is \\
11 & 28 & chapter 5 & Chapter 5 \\
12 & 6 & chapter 6 & Chapter 6 \\
22 & 15 & RadarSat & RadarSat-2 \\
24 & 14 & SVM & SVM (Support Vector Machine) \\
35 & 6-7 & Rician distribution [48]... & Rician distribution [48]. \\
35 & 11 & back scattering & backscattering \\
36 & 10 & literatured & literatures \\
37 & -2 & Proposed bu & proposed by \\
39 & 4 & dependence & dependency \\
44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
46 & 4 & most known common & most commonly known \\
56 & 6 & POLSAR And & POLSAR. And \\
65 &5,7 & an homogeneous area & a homogeneous area \\
77 & 3 & the objective then is & the objective is \\
77 & 5,6 & it has already been proven & it has already been proven [?] \\
87 & -1 & Fig 5.6a & Fig 5.6. \\
89 & - & Figure 5.6 - subtitle (a) & (a) is removed \\
91 & - & Figure 5.8: Legends are too small to read & They are enlarged \\
95 & - & Figure 5.12 & Use the same scale for  y axis (i.e MSE 0:1) across all the plots \\
103 & 22 & related to the ENL index. over & related to the ENL index over \\
104 & 13 & Equation 5.3.2.1 & The number is corrected to (?) \\
109 & 8 & Figs. 5.21c and 5.21d allows & Fig 5.21(a) and Fig 5.21(d) allow \\
112 & 13 & these smaller requirements & these requirements \\
132 & 9 & evaluation criteria & evaluation criterion
\end{longtable}    
\rowcolors{1}{white}{}

@@

In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
I also feel encouraged by the Examiner's suggestion to extract out portions of this thesis as scientific papers for peer review, which has also been taken up and acted upon.
